Behavior Driven Development in Haskell

### 2012-06-02 paper.tex
Doctest is the solution, so we do not mention it in "Problems" anymore.
simplify

\subsection{Doctest and Haddock}
\label{sec:doctest-haddock}

@@

So, we need common syntax to describe examples and properties
independently in Haddock. Doctest should automatically verify
examples and test properties.

@@

Hspec provides an EDSL for defining specs.  A spec organizes evidence
in a tree structure (or a forest, to be accurate), and it is defined
with \texttt{it} and \texttt{describe}.

>>>>

\subsection{Haddock}
\label{sec:doctest-haddock}

@@

@@

Hspec provides an EDSL for defining specs.  A spec organizes evidence
in a tree structure (or a forest, to be accurate), and is defined
with \texttt{it} and \texttt{describe}.
